\begin{thebibliography}{10}

\bibitem{netfpga} Website de NetFPGA: http://netfpga.org/

\bibitem{click} Website de Click Router: http://www.read.cs.ucla.edu/click/click

\bibitem{fifo} Open Cores. Proyecto Versatile FIFO:

http://opencores.org/project,versatile\_fifo

\bibitem{Varghese} George Varghese. \textit{Network Algorithmics: An interdisciplinary approach to designing fast networed devices}. Morgan Kaufmann Publishers. 2005 

\bibitem{CLassif}Yaxuan Qi, Jeffrey Fong, Weirong Jiang, Bo Xu, Jun Li, Viktor Prasanna. \textit{Multi-dimensional Packet Classification on FPGA: 100 Gbps and Beyond}. International Conference on Field-Programmable Technology (FPT '10), Pekín. 2010

\bibitem{jumbo} Greg Ferro. \textit{Ethernet Jumbo Frames, Full Duplex and Why Jumbo Frames Are 9000 Bytes}. 2011

\bibitem{terabit}Amit Singhal, Raj Jain. \textit{Terabit switching: a survey of techniques and current products}. Computer Communications, vol 25, pp 547-556. 2002.


\bibitem{Monta} Rogelio Montañana. \textit{El nivel de red en Internet}. 2011

\bibitem{niossw} Altera Corporation. \textit{NIOS II Software Developer's Handbook}. 2011.

\bibitem{nioshw} Altera Corporation. \textit{NIOS II Hardware Development Tutorial}. 2011.

\bibitem{sopc} Altera Corporation. \textit{SOPC Builder. User Guide}. 2011.

\bibitem{avalon} Altera Corporation. \textit{Avalon Interface Specifications}. 2011.

\bibitem{spaz} Santiago Paz, Jorge Finochietto, Carlos Zerbini. \textit{Diseño de Arquitectura Hardware Reconfigurable para la Conmutación de Paquetes en Redes Virtuales Privadas}. Proyecto integrador. 2011.



\end{thebibliography}.
%\section{Distribucion Lineal}
